### 2021-02-10 docs/manuscript/PLOS-MSc-Thesis.tex
Remove acknow and authors symbols

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Elucidating multi-input processing 3-node gene regulatory
network topologies capable of generating striped gene expression patterns}
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Juan Camilo Arboleda-Rivera\textsuperscript{1\Yinyang},
Gloria Machado-Rodríguez\textsuperscript{1\Yinyang},
Boris Rodríguez-Rey\textsuperscript{2\textcurrency},
Jayson Gutiérrez\textsuperscript{3},
% Name5 Surname\textsuperscript{2\ddag},
% Name6 Surname\textsuperscript{2\ddag},
% Name7 Surname\textsuperscript{1,2,3*},
% with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Biología, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{2} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Física, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{3} Flanders Marine Institute (VLIZ), Wandelaarkaai 7, 8400 Oostende,
Belgium
% \textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
%
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
\ddag These authors also contributed equally to this work.

% Current address notes
\textcurrency Current Address: Dept/Program/Center, Universidad de Antioquia,
Medellín, Antioquia, Colombia % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address
% \textcurrency c Insert third current address

@@

% Group/Consortium Author Note
\textpilcrow Membership list can be found in the Acknowledgments section.

@@

\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Elucidating multi-input processing 3-node gene regulatory
network topologies capable of generating striped gene expression patterns}
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Juan Camilo Arboleda-Rivera\textsuperscript{1},
Gloria Machado-Rodríguez\textsuperscript{1},
Boris Rodríguez-Rey\textsuperscript{2},
Jayson Gutiérrez\textsuperscript{3},
% Name5 Surname\textsuperscript{2\ddag},
% Name6 Surname\textsuperscript{2\ddag},
% Name7 Surname\textsuperscript{1,2,3*},
% with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Biología, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{2} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Física, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{3} Flanders Marine Institute (VLIZ), Wandelaarkaai 7, 8400 Oostende,
Belgium
% \textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
%
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
% \Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
% \ddag These authors also contributed equally to this work.

% Current address notes
% \textcurrency Current Address: Dept/Program/Center, Universidad de Antioquia,
% Medellín, Antioquia, Colombia % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address
% \textcurrency c Insert third current address

@@

% Group/Consortium Author Note
% \textpilcrow Membership list can be found in the Acknowledgments section.

@@
